### 2019-03-19 tex_v4/manuscript.tex
v4

@@

	\begin{figure*}
		\centering
		\includegraphics[width=180mm]{fig1.pdf}
		\caption{\textbf{Morphology and oviposition behavior of female \textit{Curculio} weevils.} 
			\textbf{a}, Lateral habitus image of female \textit{Curculio~sayi} (Gyllenhal, 1836) featuring the elongate, strongly curved rostrum.
			\textbf{b}, Lateral view of the head of a female specimen of \textit{Curculio~longinasus} Chittenden, 1927, with major anatomical features indicated.
			\textbf{c}, Illustration of the oviposition behavior, proceeding from left to right: a female makes an incision in the host fruit, flexes the head directly over the bore hole using the front legs, then maintains tension on the snout while rotating to excavate a linear channel into the fruit. During this process, the female rostrum is bent until completely straight.
		}
		\label{fig::curculio}
	\end{figure*}

	\textit{\textbf{[NMF note: Feel that intro could be shortened by not "giving away" so many results. Maybe 3-5 phrases less in 2 final paragraphs of intro]}}
	We additionally describe the fracture mechanics of the snout, while considering how modification of the cuticle may prevent crack formation during oviposition.
	[Based on our findings, we posit that the composite profile of the rostral apex enables the snout to undergo repeated distal flexion while remaining within the elastic limits of the material, mitigating the risk of structural damage, and without evident alteration of the mechanical properties of the individual components of the cuticle across the structure and between species.]
	Accordingly, the flexibility and tensile strength of the rostrum appear to be derived \emph{exclusively} from modification of the composite architecture of the exoskeleton.
	This is the first time that a modified composite profile has been reported as a means of enhancing structural elasticity in the insect exoskeleton (though see \cite{Matsumura2017}).

@@

		\begin{figure*}
			\centering
			\includegraphics[width=180mm]{fig2.pdf}
			\caption{\textbf{Gross divisions of cuticle in the female \textit{Curculio} rostrum.}
				\textbf{a}, Scanning electron micrograph of the head capsule, in frontal view, of female \textit{Curculio~sulcatulus} (Casey, 1897), with the rostrum removed.
				\textbf{b}, Magnified view of the junction between the rostrum and head capsule, showing the division of the cuticle into two general regions: the exocuticle and the endocuticle.
			}
			\label{fig::cuticle}
		\end{figure*}

@@

		\begin{figure*}
			\centering
			\includegraphics[width=180mm]{fig3.pdf}
			\caption{\textbf{Composite profiles of rostral \textit{Curculio} cuticle.}
				\textbf{a}, Scanning electron micrograph of a fractured specimen of \textit{Curculio~humeralis} (Casey, 1897), showing that the cuticle of the rostral apex is organized as a $\pm45\degree$ angle-ply laminate.
				\textbf{b}, Scanning electron micrograph of a fractured specimen of \textit{Curculio~caryae}  (Horn, 1873), showing that the cuticle of the rostral base and head capsule has an approximately $30\degree$ stacking angle between each pair of pseudo-orthogonal plies.
				\textbf{c--d}, Semi-thin sections of cuticle from a specimen of \textit{Curculio humeralis}, stained with toluidine-blue-borax; demonstrating:
				(\textbf{c}) that the exocuticle of the rostral apex is reduced to a thin shell close to 5 \,{\textmu}m thick, with the endocuticle thickened to maintain a constant laminate thickness; and,
				(\textbf{d}) that the exocuticle of the head capsule and base of the snout occupies nearly half of the through-thickness of the cuticle.
			}
			\label{fig::profile}
		\end{figure*}

@@

		\begin{figure*}
			\centering
			\includegraphics[width=180mm]{fig4.pdf}
			\caption{\textbf{Tensile properties of the female \textit{Curculio} rostrum.}
				Each plot shows the relationship between two variables as predicted by a phylogenetic linear mixed-effect model; with species as a random effect and a variance-covariance matrix generated from Brownian motion over the preferred phylogeny of \cite{Bonal2016}.
				Gray regions represent the prediction interval and bootstrapped 95\% confidence interval of the model.
				The estimated fixed effect $\hat{\beta}$ is given, along with the p-value of a t-test assessing whether $\hat{\beta}$ is significantly different from zero.
				A generalized marginal $\text{R}^2_{\beta^*}$ for assessing fixed effects is also reported.
				In general, increased endocuticle thickness is associated with greater tensile strength, and stiffness is inversely correlated with toughness.
			}
			\label{fig::tensile}
		\end{figure*}

@@

		We also examined the correspondence between composite structure and mechanical behavior of the snout in an evolutionary, comparative context.
		Phylogenetic linear mixed effects models (PGLM, Fig.~\ref{fig::tensile}) were used to account for phylogenetic non-independence in residual variance, with species membership included as a random effect \cite{Revell2010, Felsenstein1985}.
		The resulting models show that the maximum force sustained at the site of failure is strongly correlated with the cross-sectional area of the endocuticle ($\hat{\beta}=1.28,~p<0.0001$), and not the exocuticle ($\hat{\beta}=0.17,~p=0.38$), at that site.
		There is thus a negative correlation between ultimate tensile strength of the specimen and the cross-sectional exocuticle-to-endocuticle area ratio at the fracture site ($\hat{\beta}=-0.36,~p=0.017$).
		Although CLPT predicts a positive association between the proportion of exocuticle and stiffness of a generalized cuticle, we found no evidence of correspondence between the cross-sectional properties of the fracture site and the overall performance of the rostrum.
		Because the cross-sectional areas of the cuticle regions vary across the length of the head along an anterior-posterior gradient, it is not possible to correlate measurements from the fracture surface to properties of the entire rostrum.
		\textit{\textbf{[NMF note: How surprising/unexpected is this? If a lot -- state so..]}}

@@

		\begin{figure*}
			\centering
			\includegraphics[width=180mm]{fig5.pdf}
			\caption{\textbf{Fatigue testing of a female \textit{Curculio caryae} rostrum.}
				\textbf{a}, Set-up of fatigue testing, with the female's head capsule fixed to a pedestal and the rostrum attached to a strip of rip-stop nylon fabric using cyanoacrylate adhesive.
				The specimen was loaded in tension, as opposed to compression, therefore isolating the effect of tension on the fatigue behavior of the rostrum.
				\textbf{b}, Overlay of the pre- and post-fatigue states of the head, showing a clear (short-term) effect from repeated prescribed strain.
				\textbf{c}, Three-photograph sequence of pre- and post-fatigue states of the rostrum; with the left and central panels showing the conditions immediately prior to and after the testing, respectively, whereas the right panel shows the head having returned to its original shape after 24 hours off soaking in a water/ethanol mixture. Hence the immediate post-fatigue shape is not permanent.
				\textbf{d}, Raw force data (left) and displacement data (right) plots for the fatigue test.
				The displacement data plot shows clear viscoelastic behavior, indicated by histeresis in the stress-strain response of the specimen, and exhibits a logarithmic decrease stress amplitude over time.
			}
			\label{fig::fatigue}
		\end{figure*}

@@

		\begin{figure*}
			\centering
			\includegraphics[width=180mm]{fig6.pdf}
			\caption{\textbf{Fractography of the female \textit{Curculio} rostrum.}
				\textbf{a}, Light micrograph showing the fracture surface of a tensile tested \textit{Curculio caryae} rostrum, displaying a typical failure mode; illustrated in (\textbf{b}):
				The small, black arrows indicate the winding direction of the macrofiber lamina; green arrows and dotted lines indicate the direction of crack.
				Scanning electron micrographs highlight: (\textbf{c}) shear cusp formation; (\textbf{d}) tensile failure and off-axis macrofiber fiber-pulling; (\textbf{e}) interlaminar delamination; (\textbf{f}-\textbf{h}) crack formation near invaginated exocuticle; and (\textbf{g}) ventral crack-front coalescence and shear cusp formation.
			}
			\label{fig::fracture}
		\end{figure*}

>>>>

	\begin{figure*}
		\centering
		\includegraphics[width=180mm]{fig1.pdf}
		\caption{\textbf{Morphology and oviposition behavior of female \textit{Curculio} weevils.} 
			\textbf{a}, Lateral habitus image of female \textit{Curculio~sayi} (Gyllenhal, 1836) featuring the elongate, strongly curved rostrum.
			\textbf{b}, Lateral view of head of female specimen of \textit{Curculio~longinasus} Chittenden, 1927, with major anatomical features indicated.
			\textbf{c}, Illustration of oviposition behavior, proceeding from left to right: female makes incision in host fruit, flexes head directly over bore-hole using front legs, then maintains tension on snout while rotating to excavate linear channel into fruit. During this process, female rostrum is bent until completely straight.
		}
		\label{fig::curculio}
	\end{figure*}

@@

	We additionally describe the fracture mechanics of the snout, while considering how modification of the cuticle may prevent crack formation during oviposition.
	Accordingly, the flexibility and tensile strength of the rostrum appear to be derived \emph{exclusively} from modification of the composite architecture of the exoskeleton.
	This is the first time that a modified composite profile has been reported as a means of enhancing structural elasticity in the insect exoskeleton (though see \cite{Matsumura2017}).

@@

		\begin{figure*}
			\centering
			\includegraphics[width=180mm]{fig2.pdf}
			\caption{\textbf{Gross divisions of cuticle in the female \textit{Curculio} rostrum.}
				\textbf{a}, Scanning electron micrograph of head capsule, in frontal view, of female \textit{Curculio~sulcatulus} (Casey, 1897), with rostrum removed.
				\textbf{b}, Magnified view of junction between rostrum and head capsule, showing division of cuticle into two general regions: exocuticle and endocuticle.
			}
			\label{fig::cuticle}
		\end{figure*}

@@

		\begin{figure*}
			\centering
			\includegraphics[width=180mm]{fig3.pdf}
			\caption{\textbf{Composite profiles of rostral \textit{Curculio} cuticle.}
				\textbf{a}, Scanning electron micrograph of fractured specimen of \textit{Curculio~humeralis} (Casey, 1897), showing that cuticle of rostral apex is organized as $\pm45\degree$ angle-ply laminate.
				\textbf{b}, Scanning electron micrograph of fractured specimen of \textit{Curculio~caryae} (Horn, 1873), showing that cuticle of rostral base and head capsule has approximately $30\degree$ stacking angle between each pair of pseudo-orthogonal plies.
				\textbf{c--d}, Semi-thin sections of cuticle from specimen of \textit{Curculio humeralis}, stained with toluidine-blue-borax; demonstrating:
				(\textbf{c}) that exocuticle of rostral apex is reduced to thin shell close to 5\,{\textmu}m thick, with endocuticle thickened to maintain a constant laminate thickness; and, 
				(\textbf{d}) that exocuticle of head capsule and base of snout occupies nearly half of through-thickness of cuticle.
			}
			\label{fig::profile}
		\end{figure*}

@@

		\begin{figure*}
			\centering
			\includegraphics[width=180mm]{fig4.pdf}
			\caption{\textbf{Tensile properties of the female \textit{Curculio} rostrum.}
				Each plot shows relationship between two variables as predicted by phylogenetic linear mixed-effect model; with species as random effect and variance-covariance matrix generated from Brownian motion over preferred phylogeny of \cite{Bonal2016}.
				Gray regions represent the prediction interval and bootstrapped 95\% confidence interval of model.
				The estimated fixed effect $\hat{\beta}$ is given, along with p-value of t-test assessing whether $\hat{\beta}$ is significantly different from zero.
				Generalized marginal $\text{R}^2_{\beta^*}$ for assessing fixed effects is also reported.
				In general, increased endocuticle thickness is associated with greater tensile strength, and stiffness is inversely correlated with toughness.
			}
			\label{fig::tensile}
		\end{figure*}

@@

		We also examined the correspondence between composite structure and mechanical behavior of the snout in an evolutionary, comparative context.
		Phylogenetic linear mixed effects models (PGLM, Fig.~\ref{fig::tensile}) were used to account for phylogenetic non-independence in residual variance, with species membership included as a random effect \cite{Revell2010, Felsenstein1985}.
		The resulting models show that the maximum force sustained at the site of failure is strongly correlated with the cross-sectional area of the endocuticle ($\hat{\beta}=1.28,~p<0.0001$), and not the exocuticle ($\hat{\beta}=0.17,~p=0.38$), at that site.
		There is thus a negative correlation between ultimate tensile strength of the specimen and the cross-sectional exocuticle-to-endocuticle area ratio at the fracture site ($\hat{\beta}=-0.36,~p=0.017$).
		Although CLPT predicts a positive association between the proportion of exocuticle and stiffness of a generalized cuticle, we found no evidence of correspondence between the cross-sectional properties of the fracture site and the overall performance of the rostrum.
		This result is not too surprising however; because the cross-sectional areas of the cuticle regions vary across the length of the head along an anterior-posterior gradient, it is not possible to correlate measurements from the fracture surface to properties of the entire rostrum.

@@

		\begin{figure*}
			\centering
			\includegraphics[width=180mm]{fig5.pdf}
			\caption{\textbf{Fatigue testing of a female \textit{Curculio caryae} rostrum.}
				\textbf{a}, Set-up of fatigue testing, with female's head capsule fixed to pedestal and rostrum attached to strip of rip-stop nylon fabric using cyanoacrylate adhesive.
				Specimen was loaded in tension, as opposed to compression, therefore isolating effect of tension on fatigue behavior of rostrum.
				\textbf{b}, Overlay of pre- and post-fatigue states of head, showing clear (short-term) effect from repeated prescribed strain.
				\textbf{c}, Three-photograph sequence of pre- and post-fatigue states of the rostrum; with left and central panels showing conditions immediately prior to and after testing, respectively, whereas right panel shows head having returned to its original shape after 24 hours off soaking in a water/ethanol mixture. Hence immediate post-fatigue shape is not permanent.
				\textbf{d}, Raw force data (left) and displacement data (right) plots for fatigue test.
				Displacement data plot shows clear viscoelastic behavior, indicated by histeresis in stress-strain response of specimen, and exhibits logarithmic decrease stress amplitude over time.
			}
			\label{fig::fatigue}
		\end{figure*}

@@

		\begin{figure*}
			\centering
			\includegraphics[width=180mm]{fig6.pdf}
			\caption{\textbf{Fractography of female \textit{Curculio} rostrum.}
				\textbf{a}, Light micrograph showing the fracture surface of tensile tested \textit{Curculio caryae} rostrum, displaying typical failure mode; illustrated in (\textbf{b}):
				Small, black arrows indicate the winding direction of macrofiber lamina; green arrows and dotted lines indicate the direction of crack.
				Scanning electron micrographs highlight: (\textbf{c}) shear cusp formation; (\textbf{d}) tensile failure and off-axis macrofiber fiber-pulling; (\textbf{e}) interlaminar delamination; (\textbf{f}-\textbf{h}) crack formation near invaginated exocuticle; and (\textbf{g}) ventral crack-front coalescence and shear cusp formation.
			}
			\label{fig::fracture}
		\end{figure*}
